```{r, message=FALSE, warning=FALSE, echo=FALSE}
# install.packages("googlesheets4")
# install.packages("testthat")
# install.packages("cobalt")
# install.packages("MatchIt")
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(data.table)
library(stargazer)
library(googlesheets4)
library(sandwich)
library(lmtest)
library(ggplot2) 
library(dplyr)
library(testthat)
library(cobalt)
library(MatchIt)
require(gridExtra)
```

# Import data  
Collect data observations from individual Google Sheets within the team's shared drive:  
```{r,  message=FALSE, warning=FALSE, echo=FALSE}
# get headers
googlelink <- "https://docs.google.com/spreadsheets/d/"
template_link <- paste0(googlelink, 
        "140ZNDM85g3AMugyb-OxnX9Tt1wf-g3mR6Jo5ZvQSTP0/edit#gid=1562913357")
data <- read_sheet(template_link, 
        sheet = 'female')

# links to each team's sheet file
teams = c(paste0(googlelink, 
                 "1H_8_uNtcyLmYfg54TcM64Bs8_qj4Cwd3X2YfdreNRss/edit#gid=1162580088"),
          paste0(googlelink, 
                 "11-cFRpcdTyqouomV5j_uVKi9GQyvA8bGHX9cjHm2P7o/edit#gid=1885686268"),
          paste0(googlelink, 
                 "12MMpX0lWgHALECGU5n7DItY0E2rcvV3jmPbI2U7cTPw/edit#gid=1001181115"),
          paste0(googlelink, 
                 "1NUEtE9yXVzikmXzmlwD0wwxdPbMBrEGtHlizUVJ3vOU/edit#gid=1562913357"))

# iterate through each team's sheet and add data to dataset
for (team in teams){
  data <- rbind(data, read_sheet(team, sheet = 'female'))
  data <- rbind(data, read_sheet(team, sheet =   'male'))
}

# drop header
data <- data[-c(1), ]

# convert to data.table
data <- data.table(data)
```

# Clean Data
## Review and analyze the 'Notes' column
```{r, cleanup the notes column}
comments <- read_sheet(paste0(googlelink, 
                  "1-M5Dj5wLSIrmJWtIxzmeEqnf1bySTMGqPIXF_jdgTP8/edit#gid=714751732"))
comments <- unique(comments)

# convert to data.table
comments <- data.table(comments)

# create analyzed_comment feature from notes columns
data <- data[comments, analyzed_comment := analyzed_comment, on = c(notes = "notes")]
```

## Encode additional variables from the data
```{r, create additional features}
# range_indicator (was a range provided?)
data <- data[ , range_provided := ifelse( !is.na(quote_range_low) & !is.na(quote_range_high), 1 , 0)]

# contacted = rows where call_attempts is not NULL 
data <- data[ , contacted := 
                ifelse( !is.na(call_attempts) , 1 , 0)]

# create outcome variable - use the mean of range if quote point is NA
data <- data[ , outcome := ifelse( is.na(quote_point), 
                                   (quote_range_low+quote_range_high)/2 , quote_point)]

# change yes/no to 1 / 0 - esl_rep and female_rep
binary_variables = c( "esl_rep", "female_rep", 
                      "script_budget_upcharge", "script_knowledge", "quote_breakdown")
for (col in binary_variables) set(data, j = col, value = +(data[[col]] == "Yes"))
```

## Create additional indicator variables
### Breakout `analyzed_comment`
```{r, create indicator variables from analyzed_comment}
# did shop return phone call (with or without quote)
data <- data[ , returned_call := 
                ifelse( analyzed_comment %in% c('returned_call_with_quote', 'returned_call_without_quote'), 1, 0)]

# indicator for failed_callback
data <- data[ , failed_callback := 
                ifelse( analyzed_comment == 'failed_callback', 1, 0)]

# indicator for does_not_perform_service
data <- data[ , does_not_perform_service := 
                ifelse( analyzed_comment == 'does_not_perform_service', 1, 0)]

# indicator for onsite_additional_info
data <- data[ , onsite_additional_info := 
                ifelse( analyzed_comment == 
                          'requires_physical_presence_or_additional_information', 1, 0)]
```

### Breakout `caller_id`-related indicator variables
```{r, create indicator variables from caller_id}
# indicator for female_caller
data <- data[ , female_caller := 
                ifelse( caller_id %in% c(1,4,5,7), 1, 0)]

# indicator for esl_caller
data <- data[ , esl_caller := 
                ifelse( caller_id %in% c(2,3,4,5,6), 1, 0)]
```

### Identify Non-Compliance and Attrition
```{r, create indicator variables for non-compliance and attrition}

# Add single no quote column where other == analyzed comment
data[ , no_quote_reason_other_cats := ifelse(no_quote_reason == "Other", analyzed_comment, no_quote_reason)]

# Make single no quote column values pretty
data[ , no_quote_reason_other_cats := recode(no_quote_reason_other_cats, "unable_to_provide_quote" = "Unable to provide quote", "failed_callback" = "Failed callback", "shop_no_longer_operating" = "Out of business", "no_phone_contact" = "No contact (after 2 tries)")]

# Add attrition indicator
data[contacted == 1, attrition := ifelse(no_quote_reason_other_cats %in% 
                     c("Refused to provide quote", 
                       "Unable to provide quote", 
                       "Failed callback"), 1, 0)]

# Add exclude indicator 
data[contacted == 1 , exclude := ifelse(no_quote_reason_other_cats %in% c("No contact (after 2 tries)", 
                                                            "Does not provide this service", 
                                                            "Out of business"), 1, 0)]
```

### Identify Affinity
```{r, create indicator variables for affinity}
# indicator for esl or gender affinity
data <- data[, esl_affinity := 
                ifelse( esl_caller == esl_rep, 1, 0) ]
data <- data[, gender_affinity := 
                ifelse( female_caller == female_rep, 1, 0) ]

# indicator for esl AND gender affinity
data <- data[, gender_esl_affinity := 
                ifelse( female_caller == female_rep & esl_caller == esl_rep, 1, 0) ]
```

## Remove Unneccessary Columns
```{r, drop unneccessary columns}
drop_cols <- c("name","address", "phone_number")
data <- data[, !c("name","address", "phone_number")]
```

```{r}
attrition_data <- data[attrition == 1]
exclude_data <- data[exclude==1]
modeling_data <- data[contacted == 1 & !is.na(outcome)]
save(data,modeling_data,attrition_data, exclude_data, file = "../raw_data.rdata")
```

```{r}
# data[enrolled_subject == 1 & treat == 1 & !is.na(outcome)]
# data[enrolled_subject == 1 & treat == 0 & !is.na(outcome)]
data[attrition == 1]
data[, unique(analyzed_comment)]
```